### 2022-10-26 manuscript.tex
Update 03.use-cases-a.md [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/9d912d5cc44030361976bccfd3cc8c304075ed06.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/9d912d5cc44030361976bccfd3cc8c304075ed06/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332378207

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267}{SORTEE-Github-Hackathon/manuscript@82d8f84}
on October 26, 2022.

@@

Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions (\protect\hyperlink{ref-1HhzKAC1K}{Goring et al., 2014}).
On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
Project management can happen via three GitHub repository features: ``Issues'', ``Discussion'' and ``Projects''.
Github Issues allow for discrete tasks and sub-tasks to be identified, assigned to team members, and categorized with custom labels.
Github Discussions serve as a message board for conversation.
Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status (\protect\hyperlink{ref-RhBKe0MG}{\emph{About Projects}, n.d.}).
Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}); \emph{Issues · Fmsabatini/sPlotOpen\_Manuscript} (\protect\hyperlink{ref-3UAritXO}{n.d.})=is\%3Aissue+is\%3Aclosed{]}.
Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).
Project management in GitHub can also be integrated with third-party applications, such as Zenhub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
Zenhub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels (see \protect\hyperlink{ref-1GRWGlDWy}{Slack, n.d.}).

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/9d912d5cc44030361976bccfd3cc8c304075ed06/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/9d912d5cc44030361976bccfd3cc8c304075ed06}{SORTEE-Github-Hackathon/manuscript@9d912d5}
on October 26, 2022.

@@

Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions (\protect\hyperlink{ref-1HhzKAC1K}{Goring et al., 2014}).
On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
Project management can happen via three GitHub repository features: ``Issues'', ``Discussion'' and ``Projects''.
Github Issues allow for discrete tasks and sub-tasks to be identified, assigned to team members, and categorized with custom labels.
Github Discussions serve as a message board for conversation.
Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status (\protect\hyperlink{ref-RhBKe0MG}{\emph{About Projects}, n.d.}).
Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository, \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}); \emph{Issues · Fmsabatini/sPlotOpen\_Manuscript} (\protect\hyperlink{ref-3UAritXO}{n.d.})=is\%3Aissue+is\%3Aclosed{]}.
Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).
Project management in GitHub can also be integrated with third-party applications, such as Zenhub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
Zenhub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels (see \protect\hyperlink{ref-1GRWGlDWy}{Slack, n.d.}).
